|

### 2025-01-14 doc/paper.qmd
Intergrated Zotero Quick Copy for BibTeX references

This assignment required a comprehensive application of skills learned throughout the course, incorporating data analysis, replication techniques, and visualization. In the future, this repository can be cloned or forked (if made public) to kickstart further projects on earnings management measures analysis. Thanks for reading!

>>>>

This assignment required a comprehensive application of programming skills and institutional knowledge gained throughout the course, integrating data analysis, replication, and visualization techniques in line with open science principles. In the future, this repository can be cloned or forked (if made public) to kickstart further projects on earnings management measures analysis. Thanks for reading!
